Argennon: A Scalable Smart Contract Platform

### 2021-07-04 tex/sections/consensus.tex
Fix an issue in the emergency forking protocol
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

Every block of the Argennon blockchain needs a certificate from both the committee of delegates and
the committee of validators. \textbf{A block is considered final after it receives both of
its certificates.} In Argennon as long as more than half of the total stake of validators is controlled by honest users,
the probability of discarding a final block is near zero even if all the delegates are malicious.

@@

Validators always choose a valid fork block over a block of the main chain. However, as we mentioned before,
a validator never signs a certificate for two different blocks with the same height. Consequently, if a validator
has already signed the block $b$ of the main chain, he will not sign the fork block and vice versa.

@@

A member of the appropriate committee will sign the certificate of a seal block only if he has not already signed
a block after the fork block (i.e., a block with the same parent as the seal block).

The seal block is not a normal block and validators who signed a certificate for a seal block are allowed
to sign a certificate for a block with the same height if the parent of that block is not the fork
block. In other words, the signers of the seal block are not allowed to sign a certificate for
any blocks on the sealed chain, but are allowed to sign certificates for other chains.

@@

The evidence which proves a committee of delegates is malicious is an invalid block that is signed by at least
one delegate:
\begin{itemize}
    \item a block that is not conditionally valid
    \item two different blocks at the same height
    \item a block that has an invalid format
\end{itemize}

>>>>

Every block of the Argennon blockchain needs a certificate from both the committee of delegates and
the committee of validators. A block is considered final after its \textbf{next} block receives \textbf{both} of
its certificates. In Argennon as long as more than half of the total stake of validators is controlled by honest users,
the probability of discarding a final block is near zero even if all the delegates are malicious.

@@

For signing a fork block, a validator ensures that the block is signed by the reserve committee and contains
a valid fork request. The parent of the fork block does not necessarily need a validators' certificate. If the
parent does not have a certificate, the validator checks the certificate of the block before the parent and
the conditional validity of the parent instead. This enables the reserve committee
to recover the liveliness of
the blockchain in a situation where a malicious committee has generated multiple blocks at the same height.

A validator always choose a valid fork block over a block of the main chain. However, as we mentioned before,
a validator never signs a certificate for two different blocks with the same height. Consequently, if a validator
has already signed the block $b$ of the main chain, he will not sign the fork block and vice versa.

@@

The seal block is not a normal block and validators who signed a certificate for a seal block are allowed
to sign a certificate for a block with the same height and vice versa. However, it should be noted that
generating a block with the same parent as the seal block is considered a malicious behaviour of the reserve
committee and validators will not sign such a block.

@@

The evidence which proves a committee of delegates is malicious is an invalid block that is signed by at least
one delegate:
\begin{itemize}
    \item a block that is not conditionally valid
    \item two different blocks with the same parent
    \item a block that has an invalid format
\end{itemize}
